### 2020-06-11 report/sections/evalconcl/eval/benchmarks.tex
Report: make graphs bigger
Report: fix bad subfig numbering

We compare the execution patterns of exchanging 10,000 Ping-Pongs
throughout 20 repeated experiments across the three implementations.
We visualise the elapsed time with respect to the number of \tmsg{PING}s
received in \cref{fig:execution}.

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=\textwidth]{execbare10000}
\caption{\texttt{bare}}
\label{fig:executionbare}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=\textwidth]{execbaresafe10000}
\caption{\texttt{bare_safe}}
\label{fig:executionbaresafe}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=\textwidth]{execmpst10000}
\caption{\texttt{mpst}}
\label{fig:executionmpst}
\end{subfigure}
\captionof{figure}{Comparison of Execution Pattern for 10,000 Ping-Pongs}
\label{fig:execution}
\end{figure}

@@

const logic = new S14({
	PING: (count) => {
		console.timeLog(LABEL, ++count);
		if (count === MSGS) {
			return new S16([Labels.S16.BYE, [count], new S15()]);
		} else {
			return new S16([Labels.S16.PONG, [count], logic]);
		}
 	}
});
\end{lstlisting}
\caption{\texttt{mpst} implementation of \tprotocol{Ping Pong} \trole{Svr}}
\label{lst:nodepingpongmpst}
\end{subfigure}
\captionof{figure}{Comparison of \texttt{bare} and \texttt{mpst}
implementations for \tprotocol{Ping Pong} \trole{Svr}}
\label{fig:nodepingpong}
\end{figure}

>>>>

We compare the execution patterns of exchanging 10,000 Ping-Pongs
throughout 20 repeated experiments across the three implementations.
We visualise the elapsed time with respect to the number of \tmsg{PING}s
received in \cref{fig:execution}: each line represents one
execution of the benchmark.

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{execbare10000}
\caption{\texttt{bare}}
\label{fig:executionbare}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{execbaresafe10000}
\caption{\texttt{bare_safe}}
\label{fig:executionbaresafe}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{execmpst10000}
\caption{\texttt{mpst}}
\label{fig:executionmpst}
\end{subfigure}
\caption{Comparison of Execution Pattern for 10,000 Ping-Pongs}
\label{fig:execution}
\end{figure}

@@

const logic = new S14({
	PING: (count) => {
		console.timeLog(LABEL, ++count);
		if (count === MSGS) {
			return new S16([Labels.S16.BYE, [count], new S15()]);
		} else {
			return new S16([Labels.S16.PONG, [count], logic]);
		}
 	}
});
\end{lstlisting}
\caption{\texttt{mpst} implementation of \tprotocol{Ping Pong} \trole{Svr}}
\label{lst:nodepingpongmpst}
\end{subfigure}
\caption{Comparison of \texttt{bare} and \texttt{mpst}
implementations for \tprotocol{Ping Pong} \trole{Svr}}
\label{fig:nodepingpong}
\end{figure}
